---
title: "Composition analysis: lexical complexity"
author: "Author 1"
date: "2023-10-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>
Hello, reader! Thank you for your interest in this work.

Let me guide you through the steps taken to conduct the statistical analyses reported on our paper.

## Preparation

**Loading libraries**

Here are the libraries that we are going to employ. If you have not already, remember to install them via `install.packages()` first.:

```{r load libraries, message=FALSE}
library(tidyverse)
library(areaplot)
library(ggthemes)
library(RColorBrewer)
library(gridExtra)
library(reshape2)
library(cowplot)

```

**Loading data sets**

Next, we are going to load the data sets obtained after computing the measures needed for our model with Python.

```{r load files, message=FALSE}
# ==== COMPOSITION ANALYSIS ====
stats_per_doc <- read_csv('Data/docs_analysis.csv')
```

**Cleaning data set**

```{r clean data sets, message=FALSE}
# Rename columns
stats_per_doc <- stats_per_doc %>%
  rename(ParticipantID = `participant_ID`,
         TextID = `text_ID`,
         TextFile = `Text file`,
         CountA1 = `Count A1`,
         CountA2 = `Count A2`,
         CountB1 = `Count B1`,
         CountB2 = `Count B2`,
         CountC1 = `Count C1`,
         CountC2 = `Count C2`,
         FreqA1 = `Freq A1`,
         FreqA2 = `Freq A2`,
         FreqB1 = `Freq B1`,
         FreqB2 = `Freq B2`,
         FreqC1 = `Freq C1`,
         FreqC2 = `Freq C2`,
         TfidfA1 = `TFIDF A1`,
         TfidfA2 = `TFIDF A2`,
         TfidfB1 = `TFIDF B1`,
         TfidfB2 = `TFIDF B2`,
         TfidfC1 = `TFIDF C1`,
         TfidfC2 = `TFIDF C2`,
         Density = `Lexical density`)

# Add a column with the composition number to better operate with the information
text_num <- rep(1:4, times = 21)
stats_per_doc$TextNum <- text_num
stats_per_doc$ParticipantID <- as.factor(stats_per_doc$ParticipantID)
stats_per_doc <- stats_per_doc %>%
  select(ParticipantID, TextID, TextNum, everything())
```

**Data visualization**

```{r data visualization, fig.width = 12, fig.height = 6, message=FALSE}

custom_palette <- c("#fff1e6", "#ffd7ba", "#eccaff", 
                    "#bdb2ff", "#ccd5ae", "#acd8aa",
                    "#fad2e1", "#c8c7d6", "#fcf6bd",
                    "#bee1e6", "#e2a0ff", "#d4a373",
                    "#d5bdaf", "#ffd972", "#faa381",
                    "#d17b88", "#fface4", "#b9fbc0",
                    "#75dbcd", "#a2d2ff", "#809bce")


# ==== Vocabulary Sophistication Stacked Bar Chart ====

stats_1 <- stats_per_doc %>%
  filter(TextNum == 1)
stats_2 <- stats_per_doc %>%
  filter(TextNum == 2)
stats_3 <- stats_per_doc %>%
  filter(TextNum == 3)
stats_4 <- stats_per_doc %>%
  filter(TextNum == 4)

mean_FreqA1_1 <- mean(stats_1$FreqA1)
mean_FreqA1_2 <- mean(stats_2$FreqA1)
mean_FreqA1_3 <- mean(stats_3$FreqA1)
mean_FreqA1_4 <- mean(stats_4$FreqA1)
mean_FreqA2_1 <- mean(stats_1$FreqA2)
mean_FreqA2_2 <- mean(stats_2$FreqA2)
mean_FreqA2_3 <- mean(stats_3$FreqA2)
mean_FreqA2_4 <- mean(stats_4$FreqA2)
mean_FreqB1_1 <- mean(stats_1$FreqB1)
mean_FreqB1_2 <- mean(stats_2$FreqB1)
mean_FreqB1_3 <- mean(stats_3$FreqB1)
mean_FreqB1_4 <- mean(stats_4$FreqB1)
mean_FreqB2_1 <- mean(stats_1$FreqB2)
mean_FreqB2_2 <- mean(stats_2$FreqB2)
mean_FreqB2_3 <- mean(stats_3$FreqB2)
mean_FreqB2_4 <- mean(stats_4$FreqB2)
mean_FreqC1_1 <- mean(stats_1$FreqC1)
mean_FreqC1_2 <- mean(stats_2$FreqC1)
mean_FreqC1_3 <- mean(stats_3$FreqC1)
mean_FreqC1_4 <- mean(stats_4$FreqC1)
mean_FreqC2_1 <- mean(stats_1$FreqC2)
mean_FreqC2_2 <- mean(stats_2$FreqC2)
mean_FreqC2_3 <- mean(stats_3$FreqC2)
mean_FreqC2_4 <- mean(stats_4$FreqC2)

rel_freq <- data.frame(
  TextNum = rep(1:4, each = 6),
  VocabLevel = rep(c("A1", "A2", "B1", "B2", "C1", "C2"), times = 4),
  Freq = c(mean_FreqA1_1, mean_FreqA2_1, mean_FreqB1_1,
           mean_FreqB2_1, mean_FreqC1_1, mean_FreqC2_1,
           mean_FreqA1_2, mean_FreqA2_2, mean_FreqB1_2,
           mean_FreqB2_2, mean_FreqC1_2, mean_FreqC2_2,
           mean_FreqA1_3, mean_FreqA2_3, mean_FreqB1_3,
           mean_FreqB2_3, mean_FreqC1_3, mean_FreqC2_3,
           mean_FreqA1_4, mean_FreqA2_4, mean_FreqB1_4,
           mean_FreqB2_4, mean_FreqC1_4, mean_FreqC2_4)
)

orderedLevels <- c("C2", "C1", "B2", "B1", "A2", "A1")

PlotFreq <- ggplot(rel_freq,
  aes(x = TextNum,
      y = Freq,
      fill = factor(VocabLevel, levels = orderedLevels))) +
  geom_bar(stat = "identity",
           position = "fill",
           color = "black",
           linewidth = 0.25) +
  geom_text(
    aes(label = round(Freq, 4)),
    size = 2,
    position = position_fill(vjust = 0.5)) +
  labs(title = "Lexical sophistication over time",
       x = "Writing task",
       y = "Mean relative frequency") +
  scale_fill_manual(values = rev(brewer.pal(6, "Pastel2"))) +
  guides(fill = guide_legend(
    title = "Vocabulary level",
    label.position = "right",
    title.theme = element_text(size = 10),
    label.theme = element_text(size = 7))) +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_text(size = 7),
        axis.text.x = element_text(size = 6),
        axis.title.x = element_text(size = 7),
        plot.title = element_text(size = 12),
        legend.position = "bottom")

# ==== Measure of Textual Lexical Diversity (MTLD) Stacked Area Chart ====

PlotMTLD <- ggplot(stats_per_doc,
                    aes(x = TextNum, y = mtld,
                        fill = ParticipantID)) +
  geom_area(colour = "black", linewidth = 0.25) +
  labs(title = "Lexical diversity over time",
       x = "Writing task\n",
       y = "MTLD") +
  scale_fill_manual(values = custom_palette) +
  guides(fill = guide_legend(
    title = "Participant",
    label.position = "right",
    title.theme = element_text(size = 10),
    label.theme = element_text(size = 7))) +
  theme(axis.text.y = element_blank(),
        axis.title.y = element_text(size = 7),
        axis.text.x = element_text(size = 6),
        axis.title.x = element_text(size = 7),
        plot.title = element_text(size = 12),
        legend.position = "bottom")

# ==== Measure of Lexical Density Heatmap ====
stats_per_doc$ParticipantID <- factor(stats_per_doc$ParticipantID, levels = rev(sort(unique(stats_per_doc$ParticipantID))))

df_wide <- dcast(stats_per_doc, ParticipantID ~ TextNum, value.var = "Density")

PlotDensity <- ggplot(melt(df_wide),
                    aes(x = variable, y = ParticipantID,
                        fill = value)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "#e2a0ff") +
  theme(axis.text.y = element_text(size = 6),
        axis.title.y = element_text(size = 7),
        axis.text.x = element_text(size = 6),
        axis.title.x = element_text(size = 7),
        plot.title = element_text(size = 12),
        legend.position = "bottom",
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 10)) +
  labs(title = "Lexical density over time", x = "Writing task", y = "Participant", fill = "Lexical density")

# Extract legends to add them later

get_legend <- function(plot) {
  tmp <- ggplotGrob(plot)
  legend <- gtable::gtable_filter(tmp, "guide-box")
  return(legend)
}

legendFreq <- get_legend(PlotFreq)
legendMTLD <- get_legend(PlotMTLD)
legendDensity <- get_legend(PlotDensity)

PlotFreq <- PlotFreq + theme(legend.position = "none",
                             panel.background = element_rect(fill = "white", color = NA),
                               panel.grid.major = element_line(color = "grey80", size = 0.5, linetype = "dashed"))
PlotMTLD <- PlotMTLD + theme(legend.position = "none",
                             panel.background = element_rect(fill = "white", color = NA),
                               panel.grid.major = element_line(color = "grey80", size = 0.3, linetype = "dashed"))
PlotDensity <- PlotDensity + theme(legend.position = "none",
                                   panel.background = element_rect(fill = "white", color = NA))

# Arrange each plot with its respective legend using grid.arrange
PlotFreq_with_legend <- arrangeGrob(PlotFreq, legendFreq, ncol = 1, heights = c(4, 1))
PlotMTLD_with_legend <- arrangeGrob(PlotMTLD, legendMTLD, ncol = 1, heights = c(4, 1))
PlotDensity_with_legend <- arrangeGrob(PlotDensity, legendDensity, ncol = 1, heights = c(4, 1))

# Arrange the three combined plots in a row
final_plot <- grid.arrange(PlotFreq_with_legend, PlotMTLD_with_legend, PlotDensity_with_legend, ncol = 3)
